Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-24 analysis/quarto/paper.tex
incorporate comments on citation, style and punctuation

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Replication study, Non-convenience sample, Open
science, Dynamic public good game, Online experiment, Generalizability},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{abstract}
I revisit the dynamic public good game by Gächter et al.~(2017)
developed to study cooperation under dynamic interdependencies.
Collecting data from both a convenient (students) and an inconvenient
(general population) sample, I not only reproduce some of the author's
original observations but also test their novel game's generalizability.
Appending a charitable dictator game, I find no correlations between
behavior in the charitable context and the dynamic game. This applies to
students and the general population sample alike. Because the study of
inexperiend general population samples raises methodological challenges,
such as fatigue and dropouts, this research approaches them. Doing so, I
and provide simple solutions to run relieable interactive experiments
online.

@@

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

Public good (or public bad) games---although often intended to inform
climate policies (e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
interdependencies simply because participants have the same set of
actions in each period. Accordingly, participants' actions in a given
period do not affect their number of actions in subsequent periods. To
see the lack of realism, consider carbon dioxide emissions, where the
current stock will last for well over a millennium
\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
each period is as if one could just undo carbon dioxide emissions at no
cost.

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
shows that it is fairly simple to remedy that flaw. They incorporated
interdependencies into a \emph{dynamic} public good game by defining
endowments as the income of previous periods. To put it differently,
participants' actions in a given period affect their number of actions
in subsequent periods: the more (less) they earn now, the more (less)
they can contribute in the next period. Importantly, this modification
qualitatively yields the same rational predictions as the static game
(i.e.~free-riding and the under-provision of the public good). It is
thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on
interdependencies\footnote{One exemption are \citet{Moser2019}, who
  built on GMTV's design to investigate leadership.}, I reproduced one
of GMTV's treatments to compare dynamics across (in)experienced samples
to investigate its generalizability. \citet{GKLS2020} find that static
public good games do not generalize well to real-world climate action.
They also find that generalizability depends on structural resemblance
of the public goods game with the context of climate change mitigation:
Greater resemblance improves generalizability. Because GMTV's dynamic
setting has a more realistic property---namely, interdependencies---one
would expect it to be better suited to inform public policy. To test
this intuition, I not only ran the experiment with different samples but
also observed the participants' behavior in voluntary climate actions
(VCA).\footnote{The VCA is a (charitable) dictator games where each
  participant is a dictator dividing her budget between herself and some
  organization linked to the reduction of CO2 emissions.
  \citet{EckelGrossman1996} were the first to implement a charitable
  dictator game observing contributions of 30\% of the endowments. Like
  \citet{GKLS2020}, \citet{CarpenterEtAl2008} report that students make
  lower contributions to charity than community members.} This yielded a
setting similar to \citet{GKLS2020}'s which allows me to analyze how
behavior in the abstract game translates into real-world action across
samples. This research shows that the dynamic setting \emph{does not}
add any advances with respect to generalizability of results.

\citet{AGM2018} conducted static public good games in the lab and on
MTurk to draw lessons from online experimentation. This study extends
this literature \citep[see also][
\citet{AmirEtAl2012}]{GoodmanPaolacci2017} by focusing on an
\emph{inconvenient} sample (i.e.~one that is completely inexperienced
sample that has not been exposed to interactive experiments before)
playing a computationally more complex game. This required me to design
a robust (and thus, more complex) software to minimize attrition. I
collected paradata to assess the desired fluency and feasibility of the
experiment. This research reports on the robust design that made the
dynamic game feasible.

@@

After commenting on transparent research practices and reporting the
methods in Section~\ref{sec-transparency} and Section~\ref{sec-methods},
this paper is organized along these findings: The confirmatory
reproduction is reported in Section~\ref{sec-replication}, the online
feasibility in Section~\ref{sec-feasibility} and the generalizability in
Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
concludes.

@@

\begin{quote}
\emph{``There are two possible articles you can write: (a) the article
you planned to write when you designed your study or (b) the article
that makes the most sense now that you have seen the results. They are
rarely the same, and the correct answer is (b).''}
\end{quote}

Now, 20 years later, we accustom ourselves with mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations were established to tie the
researchers' hands when doing confirmatory research--reducing observable
discrepancies between Daryl Bem's above-mentioned (a) and (b). Today,
researchers can not only choose where to pre-register but also decide
about the level of detail they provide. More severely, nothing stops
researchers from pre-registering multiple hypotheses opposing each other
(see e.g. \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
discussion).

@@

Discussing the costs and benefits of pre-registrations,
\citet{Olken2015} stresses the uncertainty of research processes and
promotes moderate approaches. As \citet{WaldronAllen2022}, he argues
that pre-registrations not necessarily eliminate flexibility. These
`moderate' or `flexible' approaches require transparency to reduce
concerns of \emph{`data-mining'} \citep[ p.~61]{Olken2015} by showing
(a) the analyses I planned to run, (b) the analysis that made most sense
after collecting the data and the transition from (a) to (b). Because
this is neither incentivized nor easy to verify, we need tools that make
transparency convenient to establish and to scrutinize. I propose
version control (such as Git) as one such tool and illustrate its
application on this paper: GitHub is a website and cloud-based service
where developers---and researchers alike---can store and manage their
code. The service is based on Git\footnote{Git is a specific open-source
  version control system developed in 2005.} and designed for version
control. Importantly, changes are time-stamped and can be tracked.
Moreover, one can create branches, that is, duplicates of code -- either
to work collaborative or to archive a certain state.

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific} reproduction\footnote{\citet{Parsons2022}
  use the term of a \emph{conceptual replication} which means the same.}
of one treatment of GMTV's dynamic public good game. The pure
reproduction re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
reproduction, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

\begin{quote}
\emph{``subjects are divided into groups and play the same game for a
finite number of periods. Each period, every subject is endowed with an
income {[}\ldots{]} The subject must then divide this income between a
contribution to a private account {[}\ldots{]} that yields a constant
return to themselves only and a contribution to a public account
{[}\ldots{]} where consumption benefits accrue to all group members. At
the end of each period, subjects typically learn the aggregate
contribution to the public good by all members of their group and their
earnings for the period.''}
\end{quote}

Considering the design, the only differences between such a
\emph{static} game (with partner matching) and GMTV's design are
\emph{dynamics}: Instead of receiving fresh endowments every period,
participants receive one endowment only at the beginning of the first
period. A participant's endowment in the second period is the wealth she
accumulated in the first period. A participant's endowment in the third
period is the wealth she accumulated in the first two periods. And so
on. Hence, a decision in one period has consequences on future
endowments and, ultimately, growth paths. For this reason, the game is
described as a \emph{dynamic} public good game.

@@

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
participants could donate any amount their earnings to offset carbon
dioxide (that is, retire emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were to be
posted immediately after the concluding the sessions online. To avoid
privacy or social image concerns, participants learned their unique and
random IDs, which they needed to identify their individual
contributions. The document certified that their contributions have been
used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

While I stuck to GMTV's protocol as close as possible, I deviated in a
few aspects. First, the instructions were German and also covered topics
inherent to the online setting (dropouts and bots, for instance).
Second, I used another software (oTree instead of zTree) which also
affected the graphical user interface participants were exposed to.
Third, GMTV gave participants the opportunity to donate to \emph{Doctors
without Borders} whereas we offered carbon dioxide offsets.

@@

First, I ask whether the samples differ with respect to their initial
contributions to the public good. Is the reproduction sample (consisting
of both students and non-students) more pro-social than the original
sample? A two-sided rank sum test reveals that it is not (p=0.3926).
Both samples contributed 10 tokens, that is, 50\% of their endowments on
average (median and mean). Moreover, both samples' initial contributions
resemble initial contributions participants usually make in the static
game with partner matching.\footnote{See Figure 3B in
  \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
dynamic game presented here, we are particularly interested in the
subsequent periods because differences add up exponentially. Do the two
groups remain similar over the course of time?

@@

How do the different contribution-paths translate into
wealth?\footnote{To measure wealth and growth, I define a variable
  called \emph{stock} which sums the endowments of all participants in a
  given group at the end of the round (that is, after the contributions
  have been made, multiplied and redistributed).} Given that the
original sample contributed more, one would expect the respective groups
to be more wealthy. A mere mean comparison indicates just that: An
average group in the original sample accumulated about 478 tokens. In
contrast, an average group in the reproduction sample accumulated about
380 tokens. This difference is insignificant at conventional levels
though: A two-sided rank sum test (comparing differences between
samples) yields a p-Value of 0.1356 for the mean stock in last period of
the game.

@@

Given the different samples and the possibility of endogenous
growth--which essentially is the main feature of the game--I ask whether
and how the inequality grows \emph{within} groups.
Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
at the end of the game, the original and the replication groups exhibit
an average Gini coefficient of 0.23 and 0.22, respectively.\footnote{The
  two-sided rank sum test (comparing differences between samples) yields
  a p-Value of 0.6059 for the mean Gini coefficient in last round of the
  game.} Because every participant started with the same initial
endowment (in \emph{period 0}, so to speak), every group started
equally--with a Gini coefficient equaling zero.

@@

\citet{GKLS2020} asked how much can we learn about voluntary climate
action from the behavior in public goods games. Using a similar
strategy, I answer the question for a \emph{dynamic} public good game:
\emph{Not much}. Overall, there seems to be no association between
choices in the voluntary climate action and the first period in the
dynamic public goods game.

Figure~\ref{fig-kernel-generalizability} shows distributions of
contributions across both choices for both samples. The top panels
illustrate the behavior of the general population sample. The bottom
panels illustrate the behavior of the student sample. The left panels
show the behavior in the VCA. The right panels show the behavior in
first period of the game. A visual inspection shows that (a) mean
contributions are positive in both tasks for both samples.\footnote{The
  same holds true for median contributions.} (b) Furthermore, average
contributions are lower in the VCA. (c) In contrast to
\citet{GKLS2020}'s observation, we do not observe a difference between
samples in the abstract game's contribution behavior. (d) However, the
student's share of income contributed to the VCA is significantly lower
than the general population sample's contributions (two-sided rank sum
test, p=0.0085). Taken together, these aggregate results indicate, that
the consistency between tasks is higher for the general population than
it is for students. Or, to put it differently, the general population's
behavior in the abstract game better predicts their behavior in
real-world mitigation context.

@@

Table~\ref{tbl-tobit-generalizability} shows that this is not the case.
It reports tobit regression results cautioning against transferability
from dPGG results to real-world mitigation behavior: The share of
endowment contributed in the first period (displayed in the first row)
does not predict the share of earnings donated as a VCA. The student
status negatively affects VCA donations in column two but disappears if
one controls for age in column three. Importantly, the interaction of
student status and first-period contributions is not significant. This
suggests that the general population sample's transferability is just as
bad as the student sample's. We thus, find a similar result as
\citet[p.6]{GKLS2020}.

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Journal of Behavioral and Experimental Economics}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation},
  pdfauthor={Hauke Roggenkamp},
  pdfkeywords={Replication study, Non-convenience sample, Open
science, Dynamic public goods game, Online
experiment, Generalizability},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{abstract}
I revisit the dynamic public goods game by Gächter et al.~(2017)
developed to study cooperation under dynamic interdependencies.
Collecting data from both a convenient (students) and an inconvenient
(general population) sample, I not only reproduce some of the author's
original observations but also test their novel game's generalizability.
Appending a charitable dictator game, I find no correlations between
behavior in the charitable context and the dynamic game. This applies to
students and the general population sample alike. Because the study of
inexperiend general population samples raises methodological challenges,
such as fatigue and dropouts, this research approaches them. Doing so, I
provide simple solutions to run relieable interactive experiments
online.

@@

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public goods game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

Public good (or public bad) games---although often intended to inform
climate policies (e.g. \citet{MilinskiEtAl2006}, \citet{TavoniEtAl2011},
\citet{Hauser2014}, \citet{BrickEtAl2015}, \citet{GomezEtAl2018},
\citet{CalzolariEtAl2018}, \citet{CookEtAl2019})---miss these temporal
interdependencies simply because participants have the same set of
actions in each period. Accordingly, participants' actions in a given
period do not affect their action space in subsequent periods. To see
the lack of realism, consider carbon dioxide emissions, where the
current stock will last for well over a millennium
\citep{Inman2008, CalzolariEtAl2018}. Playing with fresh endowments in
each period is as if one could just undo carbon dioxide emissions at no
cost.

A game designed by Gächter, Mengel, Tsakas \& Vostroknutov \citeyearpar[
hereafter, GMTV]{GMTV2017} as well as Stefan Große (2011, unpublished)
shows that it is fairly simple to remedy that limitation. They
incorporated interdependencies into a \emph{dynamic} public goods game
by defining endowments as the income of previous periods. To put it
differently, participants' actions in a given period affect their number
of actions in subsequent periods: the more (less) they earn now, the
more (less) they can contribute in the next period. Importantly, this
modification qualitatively yields the same rational predictions as the
static game (i.e.~free-riding and the under-provision of the public
good). It is thus, equally well suited to study dilemma situations.

Because there is surprisingly little experimental research on
interdependencies\footnote{One exemption are \citet{Moser2019}, who
  built on GMTV's design to investigate leadership.}, I reproduced one
of GMTV's treatments to compare dynamics across (in)experienced samples
to investigate its generalizability. \citet{GKLS2020} find that static
public goods games do not generalize well to real-world climate action.
They also find that generalizability depends on structural resemblance
of the public goods game with the context of climate change mitigation:
Greater resemblance improves generalizability. Because GMTV's dynamic
setting has a more realistic property---namely, interdependencies---one
would expect it to be better suited to inform public policy. To test
this intuition, I not only ran the experiment with different samples but
also observed the participants' behavior in voluntary climate actions
(VCA).\footnote{The VCA is a (charitable) dictator game where each
  participant is a dictator dividing her budget between herself and some
  organization linked to the reduction of CO2 emissions.
  \citet{EckelGrossman1996} were the first to implement a charitable
  dictator game observing contributions of 30\% of the endowments. Like
  \citet{GKLS2020}, \citet{CarpenterEtAl2008} report that students make
  lower contributions to charity than community members.} This yielded a
setting similar to \citet{GKLS2020}'s which allows me to analyze how
behavior in the abstract game translates into real-world action across
samples. This research shows that the dynamic setting \emph{does not}
add any advances with respect to generalizability of results.

\citet{AGM2018} conducted static public goods games in the lab and on
MTurk to draw lessons from online experimentation. This study extends
this literature
\citetext{\citealp[see][]{GoodmanPaolacci2017}; \citealp[also][]{AmirEtAl2012}}
by focusing on an \emph{inconvenient} sample (i.e.~one that is
completely inexperienced sample that has not been exposed to interactive
experiments before) playing a computationally more complex game. This
required me to design a robust (and thus, more complex) software to
minimize attrition. I collected paradata to assess the desired fluency
and feasibility of the experiment. This research reports on the robust
design that made the dynamic game feasible.

@@

After commenting on transparent research practices and reporting the
methods in Section~\ref{sec-transparency} and Section~\ref{sec-methods},
this paper is organized along these findings: The confirmatory
reproduction is reported in Section~\ref{sec-replication}, the online
feasibility in Section~\ref{sec-feasibility} and the generalizability in
Section~\ref{sec-generalizability}. Section~\ref{sec-conclusion}
concludes. Because I observed some differences in reproducing GMTV's
analysis using their data, I report these in the
\href{@sec-appendix}{Appendix}.

@@

\begin{quote}
\emph{There are two possible articles you can write: (a) the article you
planned to write when you designed your study or (b) the article that
makes the most sense now that you have seen the results. They are rarely
the same, and the correct answer is (b).}
\end{quote}

Now, 20 years later, we accustom ourselves with mechanisms designed to
unravel the fuzzy back-and-forth between exploratory and confirmatory
research. Prominently, pre-registrations were established to tie the
researchers' hands when doing confirmatory research--reducing observable
discrepancies between Daryl Bem's above-mentioned (a) and (b). Today,
researchers can not only choose where to pre-register but also decide
about the level of detail they provide. More severely, nothing stops
researchers from pre-registering multiple hypotheses opposing each other
(see, e.g., \citet{SimmonsEtAl2021} and \citet{PhamEtAl2021} for a
discussion).

@@

Discussing the costs and benefits of pre-registrations,
\citet{Olken2015} stresses the uncertainty of research processes and
promotes moderate approaches. As \citet{WaldronAllen2022}, he argues
that pre-registrations not necessarily eliminate flexibility. These
`moderate' or `flexible' approaches require transparency to reduce
concerns of \emph{`data-mining'} \citep[ p.~61]{Olken2015} by showing
(a) the analyses I planned to run, (b) the analysis that made most sense
after collecting the data and the transition from (a) to (b). Because
this is neither incentivized nor easy to verify, we need tools that make
transparency convenient to establish and to scrutinize. I propose
version control (such as Git) as one such tool and illustrate its
application on this paper: GitHub is a website and cloud-based service
where developers---and researchers alike---can store and manage their
code. The service is based on Git\footnote{Git is a specific open-source
  version control system developed in 2005.} and designed for version
control. Importantly, changes are time-stamped and can be tracked.
Moreover, one can create branches, that is, duplicates of code either to
work collaboratively or to archive a certain state.

@@

In the terminology of \citet{Hamermesh2007}, I ran both a \emph{pure} as
well as a \emph{scientific} reproduction\footnote{\citet{Parsons2022}
  use the term of a \emph{conceptual replication} which means the same.}
of one treatment of GMTV's dynamic public goods game. The pure
reproduction re-analyzes the original data.
\protect\hyperlink{A:-Pure-Replication}{Appendix A} documents
\href{}{errors I identified} in the original paper. The scientific
reproduction, where I utilize a different sample drawn from a different
population in a different situation, is described in the following
sections.

@@

\begin{quote}
\emph{subjects are divided into groups and play the same game for a
finite number of periods. Each period, every subject is endowed with an
income {[}\ldots{]} The subject must then divide this income between a
contribution to a private account {[}\ldots{]} that yields a constant
return to themselves only and a contribution to a public account
{[}\ldots{]} where consumption benefits accrue to all group members. At
the end of each period, subjects typically learn the aggregate
contribution to the public good by all members of their group and their
earnings for the period.}
\end{quote}

Considering the design, the only differences between such a
\emph{static} game (with partner matching) and GMTV's design are
\emph{dynamics}: Instead of receiving fresh endowments every period,
participants receive one endowment only at the beginning of the first
period. A participant's endowment in the second period is the wealth she
accumulated in the first period. A participant's endowment in the third
period is the wealth she accumulated in the first two periods. And so
on. Hence, a decision in one period has consequences on future
endowments and, ultimately, growth paths. For this reason, the game is
described as a \emph{dynamic} public goods game.

@@

Like GMTV I employ a real giving task after the abstract game.
Specifically, I employed a (charitable) dictator game where each
participant is a dictator dividing her budget between herself and some
organization. Whereas GMTV chose \emph{Doctors without Borders} as a
receiver, I chose another organization in another context: like
\citet{GKLS2020}, I employed a VCA, where participants could donate any
amount their earnings to offset carbon dioxide (that is, retire emission
permits from the EU ETS).\footnote{Importantly, \citet{GKLS2020} made
  the VCA decision with a fresh endowment \emph{before} they played the
  abstract game. I deviate from their procedure to match GMTV's
  procedure.} To ensure that each participant had the same basic level
of information about the impact of their decision, I provided some basic
information about the mechanism. The information also highlighted that
the mitigation came into operation on a European level. Finally, I
informed the participants that the documentation of individual and
aggregate contributions were to be posted immediately after the
concluding the sessions online. To avoid privacy or social image
concerns, participants learned their unique and random IDs, which they
needed to identify their individual contributions. The document
certified that their contributions have been used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

While I stuck to GMTV's protocol as close as possible, I deviated in a
few aspects. First, the instructions were German and also covered topics
inherent to the online setting (dropouts and bots, for instance).
Second, I used another software (oTree instead of zTree) which also
affected the graphical user interface participants were exposed to.
Third, GMTV gave participants the opportunity to donate to \emph{Doctors
without Borders} whereas I offered carbon dioxide offsets.

@@

First, I ask whether the samples differ with respect to their initial
contributions to the public good. Is the reproduction sample (consisting
of both students and non-students) more pro-social than the original
sample? A two-sided rank sum test reveals that it is not (p=0.3926).
Both samples contributed 10 tokens, that is, 50\% of their endowments on
average (median and mean). Moreover, both samples' initial contributions
resemble initial contributions participants usually make in the static
game with partner matching.\footnote{See Figure 3B in
  \citet[p.989]{fehrgaechter2000}, for instance.} However, in the
dynamic game presented here, I are particularly interested in the
subsequent periods because differences add up exponentially. Do the two
groups remain similar over the course of time?

@@

How do the different contribution-paths translate into
wealth?\footnote{To measure wealth and growth, I define a variable
  called \emph{stock} which sums the endowments of all participants in a
  given group at the end of the round (that is, after the contributions
  have been made, multiplied and redistributed).} Given that the
original sample contributed more, one would expect the respective groups
to be more wealthy. A mere mean comparison indicates just that: An
average group in the original sample accumulated about 478 tokens. In
contrast, an average group in the reproduction sample accumulated about
380 tokens. This difference is insignificant at conventional levels
though: A two-sided rank sum test (comparing differences between
samples) yields p=0.1356 for the mean stock in last period of the game.

@@

Given the different samples and the possibility of endogenous
growth--which essentially is the main feature of the game--I ask whether
and how the inequality grows \emph{within} groups.
Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
at the end of the game, the original and the replication groups exhibit
an average Gini coefficient of 0.23 and 0.22, respectively.\footnote{The
  two-sided rank sum test (comparing differences between samples) yields
  p=0.6059 for the mean Gini coefficient in last round of the game.}
Because every participant started with the same initial endowment (in
\emph{period 0}, so to speak), every group started equally--with a Gini
coefficient equaling zero.

@@

\citet{GKLS2020} asked how much can we learn about voluntary climate
action from the behavior in public goods games. Using a similar
strategy, I answer the question for a \emph{dynamic} public goods game:
\emph{Not much}. Overall, there seems to be no association between
choices in the voluntary climate action and the first period in the
dynamic public goods game.

Figure~\ref{fig-kernel-generalizability} shows distributions of
contributions across both choices for both samples. The top panels
illustrate the behavior of the general population sample. The bottom
panels illustrate the behavior of the student sample. The left panels
show the behavior in the VCA. The right panels show the behavior in
first period of the game. A visual inspection shows that (a) mean
contributions are positive in both tasks for both samples.\footnote{The
  same holds true for median contributions.} (b) Furthermore, average
contributions are lower in the VCA. (c) In contrast to
\citet{GKLS2020}'s observation, I do not observe a difference between
samples in the abstract game's contribution behavior. (d) However, the
student's share of income contributed to the VCA is significantly lower
than the general population sample's contributions (two-sided rank sum
test, p=0.0085). Taken together, these aggregate results indicate, that
the consistency between tasks is higher for the general population than
it is for students. Or, to put it differently, the general population's
behavior in the abstract game better predicts their behavior in
real-world mitigation context.

@@

Table~\ref{tbl-tobit-generalizability} shows that this is not the case.
It reports tobit regression results cautioning against transferability
from dPGG results to real-world mitigation behavior: The share of
endowment contributed in the first period (displayed in the first row)
does not predict the share of earnings donated as a VCA. The student
status negatively affects VCA donations in column two but disappears if
one controls for age in column three. Importantly, the interaction of
student status and first-period contributions is not significant. This
suggests that the general population sample's transferability is just as
bad as the student sample's. I thus, find a similar result as
\citet[p.6]{GKLS2020}.
